---
title: "Project Report"
author: "Eduardo Solano-Salgado (100351079), Tuan Anh Nguyen (100348136), Benjamin Esene (100350791), Lishu Gu (100350781), Tinh Lo (100345588)"
date: "02/04/2020"
output: html_document
---
```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

### Input the Worldcup data and data change for chisq for SAS code

    FILENAME REFFILE
    '/folders/myfolders/sasuser.v94/top100rank.xlsx';
    PROC IMPORT DATAFILE=REFFILE
    	DBMS=XLSX
    	OUT=WORLDCUP;
    	GETNAMES=YES;
    RUN;

    FILENAME REFFILE
    '/folders/myfolders/sasuser.v94/Data_for_chi_sqr_test.xlsx';
    PROC IMPORT DATAFILE=REFFILE
    	DBMS=XLSX
    	OUT=CHISQ1;
    	GETNAMES=YES;
    RUN;

### Univariate Data Analysis

```{r, echo=FALSE}
library(readxl, logical.return=FALSE)
library(ggplot2, logical.return=FALSE)
library(dplyr, warn.conflicts=FALSE)
library(MASS, logical.return=FALSE, warn.conflicts = FALSE)
```


```{r}
# Import World Cup data
WC<- read_xlsx('top100rank.xlsx')
attach(WC)
```

##### World Cup Appearances Analysis

```{r}
hist(Appearances, breaks = 10)
boxplot(Appearances, horizontal=TRUE, main = 'Boxplot of Appearances')
summary(Appearances)
quantile(Appearances)
```

##### GDP Analysis

```{r}
hist(GDP)
boxplot(GDP, horizontal = TRUE, na.rm = TRUE, main = 'Boxplot of GDP')
summary(GDP, na.rm = TRUE)
quantile(GDP, na.rm =TRUE)
```

##### Star players Analysis

```{r}
hist(Stars)
boxplot(Stars, horizontal = TRUE, main = 'Boxplot of Star Players')
summary(Stars)
quantile(Stars)
```

##### Confederation Analysis (SAS Code)


    PROC FREQ DATA = WORLDCUP;
    	TABLE CONFEDERATION / NOROW NOCOL NOCUM;
    RUN; 
    PROC SGPLOT DATA = WORLDCUP;
    	VBAR CONFEDERATION;
    	TITLE 'Frequency of Confederation';
    RUN;
    
    PROC TEMPLATE;
       DEFINE STATGRAPH CONFEDERATION;
          BEGINGRAPH;
             LAYOUT REGION;
                PIECHART CATEGORY = CONFEDERATION /
                DATALABELLOCATION = OUTSIDE
                CATEGORYDIRECTION = CLOCKWISE
                START = 180 NAME = 'pie';
                DISCRETELEGEND 'pie' /
                TITLE = 'Confederation';
             ENDLAYOUT;
          ENDGRAPH;
       END;
    RUN;
    
    PROC SGRENDER DATA = WORLDCUP
                TEMPLATE = CONFEDERATION;
    RUN;


##### Results Analysis (SAS Code)

    PROC FREQ DATA = WORLDCUP;
    	TABLE RESULT / NOROW NOCOL NOCUM;
    RUN;
    
    PROC SGPLOT DATA = WORLDCUP;
    	VBAR RESULT;
    	TITLE 'Frequency of Result';
    RUN;
    
    PROC TEMPLATE;
       DEFINE STATGRAPH RESULT;
          BEGINGRAPH;
             LAYOUT REGION;
                PIECHART CATEGORY = RESULT /
                DATALABELLOCATION = OUTSIDE
                CATEGORYDIRECTION = CLOCKWISE
                START = 180 NAME = 'pie';
                DISCRETELEGEND 'pie' /
                TITLE = 'Results';
             ENDLAYOUT;
          ENDGRAPH;
       END;
    RUN;

    PROC SGRENDER DATA = WORLDCUP
                TEMPLATE = RESULT;
    RUN;

##### Wins (SAS Code)

    PROC FREQ DATA = WORLDCUP;
    	TABLE WINS / NOROW NOCOL NOCUM;
    RUN;

    PROC SGPLOT DATA = WORLDCUP;
    	VBAR WINS;
    	TITLE 'Frequency of Win';
    RUN;

### Bivariate Data Analysis

##### Appearances and Number of Star Players

```{r}
z <- lm(Stars~Appearances,data=WC)
summary(z)
ggplot(WC)+ 
  aes(Appearances,Stars) +
  geom_point(size = 3, shape = 16) +
  geom_smooth(method = 'lm', se = F)

cor(Stars, Appearances)

#regression analysis
residual=resid(z) ## Obtain residuals
stu.residual = studres(z) ## Obtain Studentized residuals
plot(Appearances, stu.residual , ylab="Residuals", xlab="Stars", main="Studentized Residual
Plot")
abline(h=c(-2,0,2), col=c("red", "blue", "red"), lty=c(2,1,2), lwd=c(3,2,3))
hist(stu.residual, prob =T)
curve(dnorm(x, mean=mean(stu.residual), sd=sd(stu.residual)), col="darkblue", lwd=2, add=TRUE, yaxt="n")
```

##### Gross Domestic Product and Appearances at the World Cup

```{r}
m <- lm(GDP~Appearances)
summary(m)

#take out the missing values
WC.fitted <- WC %>% filter(!is.na(GDP))
m.fitted <- lm(GDP~Appearances, data = WC.fitted)
cor(WC.fitted$Appearances,WC.fitted$GDP)
summary(m.fitted)

#Scatter plot without missing values
ggplot(WC.fitted)+
  aes(WC.fitted$Appearances,WC.fitted$GDP) +
  geom_point(size = 3, shape = 16) +
  geom_smooth(method = 'lm', se = F) +
  ylab('GDP') + xlab('Appearances')
  
#regression analysis
residual1=resid(m.fitted) ## Obtain residuals
stu.residual1 =studres(m.fitted) ## Obtain Studentized residuals
plot(WC.fitted$Appearances, stu.residual1 , ylab="Residuals", xlab="Appearances", main="Studentized Residual
Plot", ylim = c(-2,2))
abline(h=c(-2,0,2), col=c("red", "blue", "red"), lty=c(2,1,2), lwd=c(3,2,3))
hist(stu.residual1, prob =T, xlim = c(-5,5))
curve(dnorm(x, mean=mean(stu.residual), sd=sd(stu.residual)), 
      col="darkblue", lwd=2, add=TRUE, yaxt="n")
```

##### Appearances and Ranking analysis

```{r}
a <- lm(Appearances ~ Ranking,data=WC)
summary(a)
ggplot(WC)+ 
  aes(Ranking,Appearances) +
  geom_point(size = 3, shape = 16) +
  geom_smooth(method = 'lm', se = F)

cor(Ranking, Appearances)

#regression analysis
residual2=resid(a) ## Obtain residuals
stu.residual2 =studres(a) ## Obtain Studentized residuals
plot(Ranking, stu.residual2 , ylab="Residuals", xlab="Ranking", main="Studentized Residual
Plot")
abline(h=c(-2,0,2), col=c("red", "blue", "red"), lty=c(2,1,2), lwd=c(3,2,3))
hist(stu.residual2, prob =T)
curve(dnorm(x, mean=mean(stu.residual2), sd=sd(stu.residual2)), 
      col="darkblue", lwd=2, add=TRUE, yaxt="n")

```

##### Ranking vs GDP

```{r}
#take out the missing values
WC.fitted <- WC %>% filter(!is.na(GDP))
m.fitted1 <- lm(GDP~Ranking, data = WC.fitted)
cor(WC.fitted$Ranking,WC.fitted$GDP)
summary(m.fitted1)

#Scatter plot without missing values
ggplot(WC.fitted)+
  aes(WC.fitted$Ranking,WC.fitted$GDP) +
  geom_point(size = 3, shape = 16) +
  geom_smooth(method = 'lm', se = F) +
  ylab('GDP') + xlab('Ranking')

#regression analysis
residual3=resid(m.fitted1) ## Obtain residuals
stu.residual3 =studres(m.fitted1) ## Obtain Studentized residuals
plot(WC.fitted$Ranking, stu.residual3 , ylab="Residuals", xlab="Ranking", main="Studentized Residual
Plot", ylim = c(-2,2))
abline(h=c(-2,0,2), col=c("red", "blue", "red"), lty=c(2,1,2), lwd=c(3,2,3))
hist(stu.residual3, prob =T, xlim = c(-5,5))
curve(dnorm(x, mean=mean(stu.residual3), sd=sd(stu.residual3)), 
      col="darkblue", lwd=2, add=TRUE, yaxt="n")

```

##### Confederation and Result (SAS Code)

    /* CHISQ TEST AND BARCHART FOR RESULT AND CONFEDERATION */
    PROC FREQ DATA = WORLDCUP;
    	TABLE RESULT * CONFEDERATION /  EXPECTED CHISQ NOROW NOCOL NOPERCENT
    	PLOTS = FREQPLOT(TWOWAY = CLUSTER SCALE = PERCENT);
    RUN;


    /* CHANGE THE TABLE IN CHISQ TEST FOR RESULT AND CONFEDERATION*/
    PROC FREQ DATA = CHISQ1;
    	TABLE RESULT * CONFEDERATION / EXPECTED CHISQ NOROW NOCOL NOPERCENT
    	PLOTS = FREQPLOT(TWOWAY = CLUSTER SCALE = PERCENT);
    RUN;

##### Confederation and Tier (SAS Code)

    /* CHISQ TEST AND BARCHART FOR RESULT AND CONFEDERATION */
    PROC FREQ DATA = WORLDCUP;
    	TABLE CONFEDERATION * TIER /  EXPECTED CHISQ NOROW NOCOL NOPERCENT
    	PLOTS = FREQPLOT(TWOWAY = CLUSTER SCALE = PERCENT);
    RUN;

    /* CHANGE THE TABLE IN CHISQ TEST FOR RESULT AND CONFEDERATION*/
    PROC FREQ DATA = CHISQ1;
    	TABLE CONFEDERATION * TIER / EXPECTED CHISQ NOROW NOCOL NOPERCENT
    	PLOTS = FREQPLOT(TWOWAY = CLUSTER SCALE = PERCENT);
    RUN;

##### Result and Tier (SAS Code)

    /* CHISQ TEST AND BARCHART FOR RESULT AND CONFEDERATION */
    PROC FREQ DATA = WORLDCUP;
    	TABLE TIER * RESULT /  EXPECTED CHISQ NOROW NOCOL NOPERCENT
    	PLOTS = FREQPLOT(TWOWAY = CLUSTER SCALE = PERCENT);
    RUN;

    /* CHANGE THE TABLE IN CHISQ TEST FOR RESULT AND CONFEDERATION*/
    PROC FREQ DATA = CHISQ1;
    	TABLE TIER * RESULT / EXPECTED CHISQ NOROW NOCOL NOPERCENT
    	PLOTS = FREQPLOT(TWOWAY = CLUSTER SCALE = PERCENT);
    RUN;