---
title: "Project Report"
author: "Eduardo Solano-Salgado"
date: "26/03/2020"
output: html_document
---
```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```
## Objective


## Introduction


## Data Source


## Analysis and Discussion


### Univariate Data Analysis

```{r}
library(readxl, logical.return=FALSE)
library(ggplot2, logical.return=FALSE)
library(dplyr, warn.conflicts=FALSE)

WC<- read_xlsx('WorldCup_top100.xlsx')
attach(WC)
```

##### World Cup Appearances Analysis
```{r}
Appearance<- pull(WC,7)

hist(Appearance, breaks = 5)
boxplot(Appearance, horizontal=TRUE)

#excluding the value
new_appr <- Appearance[Appearance!=0]
hist(new_appr, breaks = 10, xlab = 'Appearance')
boxplot(new_appr, horizontal = TRUE, xlab ='Appearance')
```
#####GDP Analysis
```{r}
GDP <- pull(WC,5)
is.na(GDP)
hist(GDP)
boxplot(GDP, horizontal = TRUE, na.rm = TRUE)
summary(GDP, na.rm = TRUE)
```
#####Star players Analysis
```{r}
star <- pull(WC,9)
hist(star)
boxplot(star, horizontal = TRUE)
summary(star)

#exclude value 0
new_star <- star[star!=0]
hist(new_star)
boxplot(new_star, horizontal = TRUE)
summary(new_star)
```
### Bivariate Data Analysis

##### Appearances and Number of Star Players
```{r}
z <- lm(Stars~Appearances,data=WC)
summary(z)
ggplot(WC)+ 
  aes(Appearances,Stars) +
  geom_point(size = 3, shape = 16) +
  geom_smooth(method = 'lm', se = F)

cor(Stars, Appearances)

#regression analysis
residual=resid(z) ## Obtain residuals
stu.residual =studres(z) ## Obtain Studentized residuals
plot(Appearances, stu.residual , ylab="Residuals", xlab="Stars", main="Studentized Residual
Plot")
abline(h=c(-2,0,2), col=c("red", "blue", "red"), lty=c(2,1,2), lwd=c(3,2,3))
hist(stu.residual, prob =T)
curve(dnorm(x, mean=mean(stu.residual), sd=sd(stu.residual)), 
      col="darkblue", lwd=2, add=TRUE, yaxt="n")
```

##### Gross Domestic Product and Appearances at the World Cup
```{r}

```
##### Input the Worldcup data and data change for chisq
```{SAS}
FILENAME REFFILE '/folders/myfolders/sasuser.v94/WorldCup.xlsx';

PROC IMPORT DATAFILE=REFFILE
	DBMS=XLSX
	OUT=WORLDCUP;
	GETNAMES=YES;
RUN;

FILENAME REFFILE '/folders/myfolders/sasuser.v94/Data_for_chi_sqr_test.xlsx';

PROC IMPORT DATAFILE=REFFILE
	DBMS=XLSX
	OUT=CHISQ;
	GETNAMES=YES;
RUN;
```
##### Confederation and Result
```{SAS}
/* CHISQ TEST AND BARCHART FOR RESULT AND CONFEDERATION */
PROC FREQ DATA = WORLDCUP;
	TABLE RESULT * CONFEDERATION /  EXPECTED CHISQ NOROW NOCOL NOPERCENT
	PLOTS = FREQPLOT(TWOWAY = CLUSTER SCALE = PERCENT);
RUN;


/* CHANGE THE TABLE IN CHISQ TEST FOR RESULT AND CONFEDERATION*/
PROC FREQ DATA = CHISQ;
	TABLE RESULT * CONFEDERATION / EXPECTED CHISQ NOROW NOCOL NOPERCENT
	PLOTS = FREQPLOT(TWOWAY = CLUSTER SCALE = PERCENT);
RUN;
```

##### Conferation and Tier
```{SAS}
/* CHISQ TEST AND BARCHART FOR RESULT AND CONFEDERATION */
PROC FREQ DATA = WORLDCUP;
	TABLE CONFEDERATION * TIER /  EXPECTED CHISQ NOROW NOCOL NOPERCENT
	PLOTS = FREQPLOT(TWOWAY = CLUSTER SCALE = PERCENT);
RUN;


/* CHANGE THE TABLE IN CHISQ TEST FOR RESULT AND CONFEDERATION*/
PROC FREQ DATA = CHISQ;
	TABLE CONFEDERATION * TIER / EXPECTED CHISQ NOROW NOCOL NOPERCENT
	PLOTS = FREQPLOT(TWOWAY = CLUSTER SCALE = PERCENT);
RUN;
```

##### Result and Tier
```{SAS}
/* CHISQ TEST AND BARCHART FOR RESULT AND CONFEDERATION */
PROC FREQ DATA = WORLDCUP;
	TABLE TIER * RESULT /  EXPECTED CHISQ NOROW NOCOL NOPERCENT
	PLOTS = FREQPLOT(TWOWAY = CLUSTER SCALE = PERCENT);
RUN;


/* CHANGE THE TABLE IN CHISQ TEST FOR RESULT AND CONFEDERATION*/
PROC FREQ DATA = CHISQ;
	TABLE TIER * RESULT / EXPECTED CHISQ NOROW NOCOL NOPERCENT
	PLOTS = FREQPLOT(TWOWAY = CLUSTER SCALE = PERCENT);
RUN;
```

## Limitations


## Conclusion
